Uranyl solvation by a three-dimensional reference interaction site model

### 2015-04-17 doc/uo2_paper/uo2-II.tex
AM: rm blue text

\begin{figure}[tbph]
\begin{centering}
\caption{Potential of mean force, $W(r)$, from the U--O$_{\text{w}}$ radial
distribution function, determined with the closure relations PSE1,
PSE2 and PSE3 (solid lines of decreasing weight). The dashed line
represents the MD result of Ref.~\citep{Bo15}\textcolor{blue}{.}
\label{fig:potential-of-mean-force}}

@@

We thank \textcolor{blue}{Prof.~H.-J.~Bungartz, his co-workers,
and Dr.\ S.\ Krüger} for valuable discussions. BL is grateful for
a fellowship by the International Graduate School of Science and Engineering
at Technische Universität München. The early stage of this work benefitted
from Dr.\ L.\ Jager making his BGY3D program package available.
This work was partially supported by Bundesministerium für Bildung
und Forschung (grant No.\ 01RC1106A).

>>>>

\begin{figure}[tbph]
\begin{centering}
\caption{Potential of mean force, $W(r)$, from the U--O$_{\text{w}}$ radial
distribution function, determined with the closure relations PSE1,
PSE2 and PSE3 (solid lines of decreasing weight). The dashed line
represents the MD result of Ref.~\citep{Bo15}.
\label{fig:potential-of-mean-force}}

@@

We thank Prof.~H.-J.~Bungartz, his co-workers,
and Dr.\ S.\ Krüger for valuable discussions. BL is grateful for
a fellowship by the International Graduate School of Science and Engineering
at Technische Universität München. The early stage of this work benefitted
from Dr.\ L.\ Jager making his BGY3D program package available.
This work was partially supported by Bundesministerium für Bildung
und Forschung (grant No.\ 01RC1106A).
